Classless Java: Tuning Java Interfaces

### 2015-11-25 paper/sections/RelatedWork.tex

\subsection{Multiple Inheritance in Object Oriented Languages}
Many authors have argued in favour or against multiple inheritance.  Multiple inheritance provides
expressive power, but it is difficult to model and implement, and can create
programs that are hard to reason about. These difficulties include the famous
diamond (fork-join) problem~\cite{bracha90mixin,Sak89dis}, conflicting methods, etc.
%and the yo-yo problem~\cite{taenzer1989problems}.  
To conciliate the need for expressive power and the need for simplicity, many
models have been proposed in over the years, including C++ virtual
inheritance, mixins~\cite{bracha90mixin} and traits~\cite{scharli03traits}.
They provide novel programming architecture models in the OO paradigm. In terms
of restrictions set on these models, C++ virtual inheritance aims at a more
general model, mixins added some restrictions on the model, and trait model is
the most restricted one (excluding states, instantiation, etc).
\bruno{How about Malayeri and Aldrich's paper? shouldn't that be discussed?}

@@

>>>>

\subsection{Multiple Inheritance in Object Oriented Languages}
Many authors have argued in favour or against multiple inheritance.  Multiple inheritance provides
expressive power, but it is difficult to model and implement, and can create
programs that are hard to reason about. These difficulties include the famous
diamond (fork-join) problem~\cite{bracha90mixin,Sak89dis}, conflicting methods, etc.
%and the yo-yo problem~\cite{taenzer1989problems}.  
To conciliate the need for expressive power and the need for simplicity, many
models have been proposed in over the years, including C++ virtual
inheritance, mixins~\cite{bracha90mixin}, traits~\cite{scharli03traits}, and
hybrid model such as CZ~\cite{malayeri2009cz}.
They provide novel programming architecture models in the OO paradigm. In terms
of restrictions set on these models, C++ virtual inheritance aims at a more
general model, mixins added some restrictions on the model, and trait model is
the most restricted one (excluding states, instantiation, etc).
\bruno{How about Malayeri and Aldrich's paper? shouldn't that be discussed?}
\yanlin{Newly added discussion on CZ. please double check.}

@@

\paragraph{CZ.}
Malayeri and Aldrich proposed a model CZ~\cite{malayeri2009cz} which aims to do
multiple inheritance without diamond problem. They divide inheritance into two
separate concepts: inheritance dependency (using \texttt{require}) and
implementation inheritance (using \texttt{extends}). Using a combination of
\texttt{requires} and \texttt{extends}, a program with diamond inheritance can be
transformed to one without diamonds. Also in this approach, fields and multiple
inheritance can coexist. However as shown in the example in the article, the
untangling of inheritance also untangles class structure. In CZ, not only the
number of classes (from 4 to 6 in the stream example), but also the class
hirarchy complexity increases. Our approach does not complicate the structure,
and (conceptual) fields coexist with multiple inheritance.
